The Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-10-30 response_to_referee.tex

\noindent \textcolor{blue}{Fig.8 caption: mention if the amplitude
  units are linear or log (the latter I think?). Also phase (radians I
  think?), although the latter has too much wrapping to be useful.}

We have added this information to the caption.

\noindent \textcolor{blue}{I suggest extracting some 1-d plots of
  amplitude and phase - these would be a great complement to the
  waterfall plots as they will contain features more difficult to see
  than on simple images.}

With the addition of figure 9, a 1D plot of the median autospectrum is
now present.  We have extracted a few 1D plots of the unwrapped phase
along the time axis (scaled by frequency), and we feel that the
results are not sufficiently interesting to add to the paper, although
we include the plot here for reference.
\begin{figure}[h]
  \vspace{-5pt}
  \begin{center}
    \includegraphics*[angle=0,width=0.5\textwidth]{Figures/unwrapped_phase_3freq.png}
  \end{center}
  \vspace{-5pt}
\end{figure}

### 2020-10-30 response_to_referee.tex

We agree that the sky is certainly not a Gaussian random field, but to
get well away from the SNR<1 regime requires that a compact source
dominate the total power coming into the antenna, not just the power
in the visibility.  For most radio telescopes this would absolutely be
a concern, but the primary beam of ALBATROS is huge.  We already know
from e.g.\ EDGES that the total power is dominated by the Galactic
signal, and in PRIZM, the Crab (and typically the sun) are not obvious
in total power.  Due to ionospheric effects ALBATROS will not
generally be conducting daytime observing, and using the GSM and Crab
fluxes in the 10-80 MHz range, we expect the Crab is only a $\sim10$\%
effect in the total power, as long as the Galaxy is not self-absorbed.
Similarly, in Fig. 8, for a 100m baseline, the visibilities seen by
ALBATROS are only a few percent of the total power.  The text in
section 4.2 has been updated to include these details.

\noindent \textcolor{blue}{The waterfall plots are all fairly
  interesting, but of not much practical value without
  calibration. What is the frequency response of the system? How much
  fainter is the RFI in the cross-correlations than the
  autocorrelations? These simple questions can be answered with a
  simple model of how the system noise changes with frequency or
  utilising the nice Galactic plane drift scans in combination with a
  crude model.}

We prefer to defer proper calibration to a future paper since the
instrumentation presented here is intended as a proof of concept, and
crude calibration that isn't fully thought out is also of limited
practical value.  The frequency response of the system is roughly
illustrated with the new addition of figure~9.  To address the
question about RFI, we have added an extra phrase in section~5
explaining that the cross-spectrum RFI is about a factor of two
fainter than the autospectrum RFI.

### 2020-10-30 albatros_paper.tex
HCC...one more comment to go...

The primary goal of the two-element pathfinder described in
\S\ref{s:2elem} was to qualitatively assess the level of RFI and
ionospheric contamination at low frequencies.
\autoref{Fig:albatros2_waterfalls} illustrates auto- and cross-spectra
from one of the co-aligned polarization pairs from the two antennas.
The data are shown over a three-day period (June 18--21, 2018), and no
calibration or cuts have been applied.  The rising and setting of the
Galaxy is visible in all of the spectrum magnitudes, and repeatable
fringes are visible in the phases of the cross-spectra.  The signal
drop-off below $\lesssim30$~MHz in the autospectra is caused largely
by the combined response of the LWA antenna and FEE, as illustrated in
\autoref{Fig:albatros2_auto_model}.  Although the LWA antenna is not
optimized for the lowest \albatros\ observing frequencies, as
described in \S\ref{s:antenna}, it is sufficient for these initial,
exploratory measurements.  The RFI lines at $\lesssim20$~MHz arise
primarily from shortwave radio transmission reflecting off the
ionosphere.  During the night, when the ionospheric plasma cutoff
frequency drops, the maximum frequency of the RFI contamination falls
to $\sim10$~MHz.

>>>>

The primary goal of the two-element pathfinder described in
\S\ref{s:2elem} was to qualitatively assess the level of RFI and
ionospheric contamination at low frequencies.
\autoref{Fig:albatros2_waterfalls} illustrates auto- and cross-spectra
from one of the co-aligned polarization pairs from the two antennas.
The data are shown over a three-day period (June 18--21, 2018), and no
calibration or cuts have been applied.  The rising and setting of the
Galaxy is visible in all of the spectrum magnitudes, and repeatable
fringes are visible in the phases of the cross-spectra.  The signal
drop-off below $\lesssim30$~MHz in the autospectra is caused largely
by the combined response of the LWA antenna and FEE, as illustrated in
\autoref{Fig:albatros2_auto_model}.  Although the LWA antenna is not
optimized for the lowest \albatros\ observing frequencies, as
described in \S\ref{s:antenna}, it is sufficient for these initial,
exploratory measurements.  The RFI lines at $\lesssim20$~MHz arise
primarily from shortwave radio transmission reflecting off the
ionosphere and are roughly a factor of two fainter in the
cross-spectrum magnitude in comparison to the autospectrum.  During
the night, when the ionospheric plasma cutoff frequency drops, the
maximum frequency of the RFI contamination falls to $\sim10$~MHz.
